Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-07-04 JCB/conclusion_JCB.tex
minor change conclusion

Our techniques are designed to correcting point-wise errors in structured regions (i.e. base paired nucleotides). Nonetheless,
our software \texttt{RNApyro} can be easily combined with other methodologies previously developed for correcting other types
of sequencing errors such as indels in unstructured regions or repeats \cite{Quinlan2008,Quince:2009uq}. In further works, we
also intend to include in our model errors stemming from insertions or deletions. It is indeed theoretically possible to considers
these scenario within our dynamic programming scheme \cite{Waldispuhl:2002fk} with minor impacts of the complexity.

>>>>

Our techniques are designed to correcting point-wise errors in structured regions (i.e. base paired nucleotides). However,
our software \texttt{RNApyro} can be easily combined with other methodologies previously developed for correcting other types
of sequencing errors such as indels in unstructured regions or repeats \cite{Quinlan2008,Quince:2009uq}. In further works, we
also intend to include in our model errors stemming from insertions or deletions. It is indeed theoretically possible to considers
these scenario within our dynamic programming scheme \cite{Waldispuhl:2002fk} with minor impacts of the complexity.
